Ceph Parallel File System Evaluation Report

### 2013-08-29 conclusion.tex
polish conclusion section

Below are our preliminary observations from mostly performance perspective:

\begin{itemize}

  \item Ceph is built on the assumption that the underlying hardware components
are unreliable, with little or no redundancy and failure detection capability.
This assumption is not valid for high-end HPC centers like ours. We have
disabled replication for pools, we haven't measured and quantified
processing overhead and we do not know yet if this would be significant.

  \item Ceph performs \textbf{metadata + data} journaling, which is fine for
host systems that has locally attached disk. However, this presents a problem
in DDN SFA10K-like hardware, where the backend LUNs are exposed as block
devices through IB over SRP protocol. The journaling write requires twice the
bandwidth compared to Lustre-like meta data-only journaling mechanism. For Ceph
to be viable in large-scale capability HPC environments like ours, journaling
operations will need to further design and engineering.

  \item We observed consistent results and linear scalability at the RADOS
level. However, we did not observe the same at the file system level. We have
experienced large performance swings during different runs, very low read
performance when transfer size is small, and I/O errors tend to happen when
system is under stress (more clients and large transfer sizes). These are not
particularly reproducible results, but it suggests that there are opportunities
for code improvement and maturation.

\end{itemize}

>>>>

Ceph is built on the assumption that the underlying hardware components
are unreliable, with little or no redundancy and failure detection capability.
This assumption is not valid for high-end HPC centers like ours. We have
disabled replication for pools, we haven't measured and quantified
processing overhead and we do not know yet if this would be significant.

Ceph performs \textbf{metadata + data} journaling, which is fine for host
systems that have locally attached disks. However, this presents a problem in
DDN SFA10K-like hardware, where the backend LUNs are exposed as block devices
through IB over SRP protocol. The journaling write requires twice the
bandwidth compared to Lustre-like meta data-only journaling mechanism. For
Ceph to be viable in large-scale capability HPC environments like ours,
journaling operations will need further design and more engineering efforts.

In our earlier tests, we experienced large performance swings during different
runs, low read performance when transfer size is small, and I/O errors tend to
happen when system is under stress (more clients and large transfer sizes).
However, with systematic performance engineering and development efforts, we
have seen a steady improvement through different releases. As of now, Ceph
system on our testbed is able to perform close to 80\% of raw hardware
capability at RADOS level and close to 70\% at file system level. This is
still no comparison to Lustre yet, but by no means a small feat for such a
\textit{young} technology. It is, in fact, a very respectable level of
performance.

%The current design on journaling write does present a challenge in
%our IB-switched storage hardware. As BTRFS and other backend file system
%mature, we are seeing promising signs for Ceph to take advantage for a
%better journaling design.
